Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-04-27 cav2017/cav2017.tex
x --> a in the description of the synthesis architecture

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .\,  \forall x.\,  \sigma(x, P)$, 
where $P$ ranges over functions, 
$x$ ranges over ground terms, 
and $\sigma$ is a quantifier-free formula.  
We interpret the ground terms over some finite domain~$\mathcal{D}$.
%
The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors {\sc inputs} that is updated incrementally.  Given
the aforementioned specification $\sigma$, the inductive synthesis
procedure tries to find an existential witness $P$ satisfying
the specification $\sigma(x, P)$ for all $x$ in {\sc
  inputs} (as opposed to all $x \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to the validation phase, which checks
whether it is a full solution (i.e., $P$ satisfies the
specification $\sigma(x, P)$ for all
$x\in\mathcal{D}$).  If this is the case, then the algorithm
terminates.  Otherwise, additional information is provided to the
inductive synthesis phase in the form of a new counterexample that is
added to the {\sc inputs} set and the loop iterates again.
More details about the general architecture of the synthesizer can
be found in~\cite{DBLP:conf/lpar/DavidKL15}.
%% It is worth noting that each iteration of the loop adds a new input to
%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
%% that the full set of inputs $\mathcal{D}$ is finite, this means that
%% the refinement loop can only iterate a finite number of times.

@@

When mapping back to the notation used for describing the general
architecture of the program synthesizer, the controller $K$ denotes $P$ and
$(x_0, u_k)$ represents $x$.

@@

For the majority of our benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach. 
However, it fails to find solutions to three benchmarks, as compared to two
with the multi-staged back-end, where the numbers given in the
discretization matrices are too small.  In direct comparison, the
abstraction-based approach is on average able to find a solution in
approximately 35\% of the time required using the multi-staged back-end, and
has a median run-time 1.15\,s, which is seven times smaller than the
multi-staged approach.  The two back-ends complement each other in benchmark
coverage and together solve all benchmarks in the set.

\begin{table}
\centering
%\scriptsize
\begin{tabular}{| r | l | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24\,s \\
2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38\,s \\
3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12\,s \\
4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39\,s \\
5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85\,s \\
6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85\,s \\
7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15\,s \\
8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9.18\,s & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8.98\,s & \xmark & \xmark \\\hline
%
\end{tabular}
\caption{Experimental results\label{tab:results}}
\end{table}

The median run-time for our benchmark set is 7.9\,s.  Overall, the average
synthesis time amounts to approximately 17.2\,s.  We consider these times
short enough to be of practical use to control engineers, and thus affirm
RQ1.

@@

The synthesized controllers were confirmed to be stable outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{a}.  \sigma(\vec{a}, \vec{P})$ 
$\exists P .\,  \forall a.\,  \sigma(a, P)$, 
where $P$ ranges over functions, 
$a$ ranges over ground terms, 
and $\sigma$ is a quantifier-free formula.  
We interpret the ground terms over some finite domain~$\mathcal{D}$.
%
The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors {\sc inputs} that is updated incrementally.  Given
the aforementioned specification $\sigma$, the inductive synthesis
procedure tries to find an existential witness $P$ satisfying
the specification $\sigma(a, P)$ for all $a$ in {\sc
  inputs} (as opposed to all $x \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to the validation phase, which checks
whether it is a full solution (i.e., $P$ satisfies the
specification $\sigma(a, P)$ for all
$x\in\mathcal{D}$).  If this is the case, then the algorithm
terminates.  Otherwise, additional information is provided to the
inductive synthesis phase in the form of a new counterexample that is
added to the {\sc inputs} set and the loop iterates again.
More details about the general architecture of the synthesizer can
be found in~\cite{DBLP:conf/lpar/DavidKL15}.
%% It is worth noting that each iteration of the loop adds a new input to
%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
%% that the full set of inputs $\mathcal{D}$ is finite, this means that
%% the refinement loop can only iterate a finite number of times.

@@

When mapping back to the notation used for describing the general
architecture of the program synthesizer, the controller $K$ denotes $P$ and
$(x_0, u_k)$ represents $a$.

@@

For the majority of our benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (9) than the multi-staged back-end (8).
In direct comparison, the
abstraction-based approach is on average able to find a solution in
approximately 70\% of the time required using the multi-staged back-end, and
has a median run-time 1.4\,s, which is seven times smaller than the
multi-staged approach.  The two back-ends complement each other in benchmark
coverage and together solve all benchmarks in the set.

\begin{table}
\centering
%\scriptsize
\begin{tabular}{| r | l | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 8.40\,s & 16,16  &   2.17\,s \\
2  & DC Motor            & 8,16   & 9.45\,s & 20,20  &   2.06\,s \\
3  & Helicopter          & \xmark & \xmark  & 16,16  &   1.37\,s \\
4  & Inverted Pendulum   & 8,16   & 9.65\,s & 16,16  &   0.56\,s \\
5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  &  44.14\,s \\
6  & Magnetic Suspension & 12,20  &10.41\,s & 16,16  &   0.61\,s \\
7  & Pendulum            & 8,16   &14.02\,s & 16,16  &   0.60\,s \\
8  & Suspension          & 12,20  &73.66\,s & \xmark &    \xmark \\
9  & Tape Driver         & 8,16   &10.10\,s & 16,16  &  68.24\,s \\
10 & Satellite           & 8,16   & 9.43\,s & 16,16  &   0.67\,s \\\hline
%
\end{tabular}
\caption{Experimental results\label{tab:results}}
\end{table}

The median run-time for our benchmark set is 9.4\,s.  Overall, the average
synthesis time amounts to approximately 15.6\,s.  We consider these times
short enough to be of practical use to control engineers, and thus affirm
RQ1.

@@

The synthesized controllers were confirmed to be stable outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance
(OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
